---
title: "Regression Models used in Group 7 Project"
output: 
  html_document:
    code_folding: hide
---

<<<<<<< HEAD
# Aims of Analysis
This RMD file outlines the final regression models used in STAT3888 Group7's 
final project. Aim was to determine the significance of nutrients on 
cardiovascular risk factors of BMI, Cholesterol and Blood Pressure.

# Description of Data
Data was sourced from the ABS's Australian Health Survey, specifically for
biomedical and nutrition. Cleaning and EDA of this data is located within 
the other Python HTML files attached.


```{r Preprocessing, warning = FALSE, message = FALSE, include = FALSE}
=======
```{r Preprocessing, message=FALSE, warning=FALSE, include=FALSE}
>>>>>>> cd1f73b6b8208d93e57e60906ed775c049a670b1
library(tidyverse)
library(skimr)
library(visdat)
library(GGally)
library(knitr)
library(corrplot)
library(glmnet)
library(brglm)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(ggplot2)
library(ggfortify)
library(jtools)
library(MASS)
library(ordinal)
library(ggfortify)
library(broom.mixed)
```

<<<<<<< HEAD

```{r Loading data, warning = FALSE, message = FALSE}
=======
```{r Loading data, warning = FALSE, message = FALSE, include = FALSE}
>>>>>>> cd1f73b6b8208d93e57e60906ed775c049a670b1
combined_data = read.csv('PC_combined_data.csv')
```

```{r Viewing combined data, warning = FALSE}
DT::datatable(combined_data)
```

```{r Viewing Systolic blood pressure, warning = FALSE}
systol_data=combined_data[ , !(names(combined_data) %in% c("X", "ABSPID", "ABSHID", "BMISC", "HCHOLBC", "CHOLRESB", "CHOLNTR", "HDLCHREB", "LDLNTR", "LDLRESB", "DIASTOL", "HSUGBC", "BMR", "EIBMR1", "EIBMR2"))] %>% 
  rename(
    Systolic.Blood.Pressure = SYSTOL,
    )
```

```{r Correlation plot of variables}
M = cor(systol_data)
png(height=1200, width=1500, pointsize=15, file="overlap.png")
corrplot(M, method = 'color', order = 'alphabet')
```

```{r SYSTOL Initial null and full models, warning = FALSE, message = FALSE}
systol_M0 = lm(Systolic.Blood.Pressure ~ 1, data = systol_data)
systol_M1 = lm(Systolic.Blood.Pressure ~ ., data = systol_data)
```

```{r SYSTOL Forward AIC on null model, warning = FALSE, message = FALSE}
systol_forw <- step(systol_M0, scope = list(lower = systol_M0, upper = systol_M1), direction = "forward", k = 2, trace = 0)
autoplot(systol_forw)
```

```{r, warning = FALSE, message = FALSE}
tab_model(systol_forw)
```

```{r, SYSTOL PLOT, echo=TRUE, fig.height= 4, fig.width= 7, warning = FALSE, message = FALSE}
plot_summs(systol_forw) + ggtitle("Regression Coefficient Estimates for Systolic Blood Pressure (95% CI)") + ylab("Predictor Variable") + xlab("Coefficient Estimate") + theme_gray(base_size = 9.5)
```

```{r Viewing bmi, warning = FALSE}
bmi_data=combined_data[ , !(names(combined_data) %in% c("X", "ABSPID", "ABSHID", "SYSTOL", "HCHOLBC", "CHOLRESB", "CHOLNTR", "HDLCHREB", "LDLNTR", "LDLRESB", "DIASTOL", "HSUGBC", "BMR", "EIBMR1", "EIBMR2"))] %>% 
  rename(
    BMI = BMISC,
    )
```

```{r BMI Initial null and full models, warning = FALSE, message = FALSE}
bmi_M0 = lm(BMI ~ 1, data = bmi_data)
bmi_M1 = lm(BMI ~ ., data = bmi_data)
```

```{r BMI Forward AIC on null model, warning = FALSE, message = FALSE}
bmi_forw <- step(bmi_M0, scope = list(lower = bmi_M0, upper = bmi_M1), direction = "forward", k = 2, trace = 0)

tab_model(bmi_forw)
```

```{r, warning = FALSE, message = FALSE}
autoplot(bmi_forw)
```

```{r BMI PLOT, warning = FALSE, message = FALSE}
plot_summs(bmi_forw) + ggtitle("Regression Coefficient Estimates for BMI (95% CI)") + ylab("Predictor Variable") + xlab("Coefficient Estimate") + theme_gray(base_size = 10)
```

```{r Viewing cholesterol, warning = FALSE}
chol_data=combined_data[ , !(names(combined_data) %in% c("X",  "ABSPID", "ABSHID", "SYSTOL", "HCHOLBC", "BMISC", "CHOLNTR", "HDLCHREB", "LDLNTR", "LDLRESB", "DIASTOL", "HSUGBC", "BMR", "EIBMR1", "EIBMR2"))] %>% 
  rename(
    Total.Cholesterol = CHOLRESB,
    )
chol_data$Total.Cholesterol = factor(chol_data$Total.Cholesterol)
```

<<<<<<< HEAD
```{r, Initial null and full models using clm() for ordinal logistic regression, warning = FALSE, message = FALSE}
chol_M0 = clm(Total.Cholesterol ~ 1,  data = chol_data, Hess = TRUE)
chol_M1 = clm(Total.Cholesterol ~ .,  data = chol_data, Hess = TRUE)
```
```{r CHOLESTEROL Forward AIC on null model, warning = FALSE, message = FALSE}
=======
```{r, Initial null and full models using clm() for ordinal logistic regression, warning = FALSE}
chol_M0 = clm(Total.Cholesterol ~ 1,  data = chol_data, Hess = TRUE)
chol_M1 = clm(Total.Cholesterol ~ .,  data = chol_data, Hess = TRUE)
```

```{r CHOLESTEROL Forward AIC on null model}
>>>>>>> cd1f73b6b8208d93e57e60906ed775c049a670b1
## Looks like forward selection does not work for ordinal logistic regression
chol_forw <- step(chol_M0, scope = list(lower = chol_M0, upper = chol_M1), direction = "forward", k = 2, trace = 0)
tab_model(chol_forw)
```

<<<<<<< HEAD
```{r, CHOLESTEROL Ordinal Regression with Features selected from Lasso Regression, warning = FALSE, message = FALSE}
chol_M2 = clm(Total.Cholesterol ~ Caffeine + Alcohol + Age + Niacin + B12 + Retinols + B6 + Risk.of.Diabetes + Folates + Starch + Fruit,  data = chol_data, Hess = TRUE)
summary(chol_M2)
```
```{r CHOLESTEROL TABLE, warning = FALSE, message = FALSE}
=======
```{r, CHOLESTEROL Ordinal Regression with Features selected from Lasso Regression, warning = FALSE}
chol_M2 = clm(Total.Cholesterol ~ Caffeine + Alcohol + Age + Niacin + B12 + Retinols + B6 + Risk.of.Diabetes + Folates + Starch + Fruit,  data = chol_data, Hess = TRUE)
summary(chol_M2)
```

```{r CHOLESTEROL TABLE}
>>>>>>> cd1f73b6b8208d93e57e60906ed775c049a670b1
tab_model(chol_M2, transform = NULL, string.est = "Estimates")
```


```{r, CHOLESTEROL PLOT, warning = FALSE, message = FALSE}
plot_summs(chol_M2) + ggtitle("Regression Coefficient Estimates for Total Cholesterol (95% CI)") + ylab("Predictor Variable") + xlab("Coefficient Estimate") + theme_gray(base_size = 10)
```



